\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{classic} % Style: classic
\moderncvcolor{blue} % Color: blue

% Adjust margins
\usepackage[scale=0.9]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}

% Personal Information
\name{David}{Kavanagh}
\email{work@dave-kav.com}
\phone[mobile]{083 427 4918}
\social[linkedin]{dave-kav}
\social[github]{dave-kav}
\homepage{dave-kav.com}

\begin{document}

% Title
\makecvtitle

% Profile Section
\section{Profile}
Senior Software Engineer with 8+ years of experience designing, developing, and deploying scalable, cloud-native software solutions. Adept at API development, distributed systems, and enhancing developer workflows. Proven leadership and management in cross-functional teams, delivering impactful projects, and driving technical excellence in dynamic environments.

% Core Skills Section
\section{Core Skills}
\cvitem{Languages}{Rust, TypeScript, JavaScript, Terraform, Java, Scala}
\cvitem{Tools}{AWS, Docker, PostgreSQL, MySQL, Redis}
\cvitem{Architecture}{Microservices, REST APIs, Event-Driven Systems}
\cvitem{DevOps}{CI/CD, IaC, Monitoring \& Logging}
\cvitem{Leadership}{Agile, Mentorship, Team Collaboration, Design}

% Experience Section
\section{Experience}
\cventry{2024--Present}{Lead Engineer, Payments}{Evervault}{Dublin, Ireland}{}{
\begin{itemize}\itemsep -2pt
    \item Lead the payments engineering team, driving technical strategy and architectural decisions for payment processing systems.
    \item Spearhead development of cloud-native applications on AWS using \textbf{Rust} for performance-critical components and \textbf{TypeScript} for server-side logic.
    \item Design and implement secure, scalable payment processing APIs, ensuring PCI compliance and robust integration with payment providers.
    \item Guide cross-team collaboration and mentor engineers while establishing best practices for system reliability and security.
\end{itemize}}

\cventry{2022--2024}{Senior Software Engineer}{Apata}{Dublin, Ireland}{}{
\begin{itemize}\itemsep -2pt
    \item Developed next-gen \textbf{Authentication and Cardholder Verification Systems} tailored for secure eCommerce transactions.
    \item Led migration of the codebase from JavaScript to \textbf{TypeScript}, enhancing code maintainability and robustness.
    \item Delivered scalable, secure architectures by leveraging \textbf{AWS} and optimizing system performance through rigorous testing.
    \item Collaborated with cross-functional teams to meet tight deadlines while maintaining technical excellence.
\end{itemize}}

\cventry{2021--2022}{Software Engineer}{Salesforce}{Dublin, Ireland}{}{
\begin{itemize}\itemsep -2pt
    \item Built interactive \textbf{Slack applications} using \textbf{TypeScript}, integrating Salesforce services to enhance user workflows.
    \item Developed backend services with \textbf{Java/Spring}, ensuring system reliability and high performance.
    \item Streamlined CI/CD processes with \textbf{Jenkins} and \textbf{Terraform}, automating deployments and infrastructure provisioning.
    \item Provided mentorship and promoted best practices in coding and architecture.
\end{itemize}}

\cventry{2017--2021}{Software Engineer - Distributed Systems}{Workday}{Dublin, Ireland}{}{
\begin{itemize}\itemsep -2pt
    \item Improved reliability and performance of distributed microservices by reducing latency and downtime.
    \item Created onboarding materials for \textbf{Scala}, accelerating team productivity and knowledge transfer.
    \item Resolved critical production issues while maintaining service-level agreements (SLAs) with minimal disruption.
    \item Contributed to architectural planning, shaping scalable and maintainable solutions.
\end{itemize}}

\cventry{2016}{Software Development Intern}{Qumas/Dassault Systèmes}{Cork, Ireland}{}{
\begin{itemize}\itemsep -2pt
    \item Prototyped solutions for efficient data ingestion and indexing using \textbf{Apache Spark} and \textbf{Kafka}.
    \item Gained hands-on experience in real-time data processing and performance optimization.
    \item Developed proof-of-concept systems for handling large-scale data streams with low latency.
\end{itemize}}

% Education Section
\section{Education}
\cventry{2025--2025}{Professional Academy Diploma in Leadership and Management}{University College Dublin}{Dublin, Ireland}{}{
\begin{itemize}\itemsep -2pt
    \item Completed an intensive leadership development program focused on modern management practices, strategic thinking, and organizational effectiveness.
    \item Developed advanced coaching and mentoring skills for team development.
    \item Enhanced communication and stakeholder management capabilities.
\end{itemize}}
\cventry{2013--2017}{Bachelor of Science in Computer Science}{Munster Technological University}{Cork, Ireland}{}{
\begin{itemize}\itemsep -2pt
    \item Graduated with First-Class Honours, specializing in distributed systems and advanced algorithms.
    \item \textbf{Final Year Project}: Designed an OCR system for retail betting, streamlining data entry and reducing manual workloads.
\end{itemize}}
\end{document}
